NewAnalysis

### 2024-11-15 Code/NewAnalysis.Rmd
added lots of qq plots at the bottom to look at

Here is the qq plot for both. It looks very similar in my opinion with only some
small differences.  I think it is reasonable to keep the gamma model.  Is it not
possible to compare the AIC's? When I try to find the AIC for log normal model
I am unable to.
```{r}
library(car)
resids_log_normal <- residuals(log_normal_model)
resids_gamma <- residuals(dash_and_hurdles_with_dq_two_effect_gamma_log)
qqPlot(resids_log_normal)
qqPlot(resids_gamma)
```

>>>>

Here is the qq plot for both. It looks very similar in my opinion with only some
small differences.  I think it is reasonable to keep the gamma model.  Is it not
possible to compare the AIC's? When I try to find the AIC for log normal model
I am unable to.
```{r}
library(car)
resids_log_normal <- residuals(log_normal_model)
resids_gamma <- residuals(dash_and_hurdles_with_dq_two_effect_gamma_log)
qqPlot(resids_log_normal)
qqPlot(resids_gamma)
```
```{r}
library(lme4)
library(lattice)
dotplot(ranef(dash_and_hurdles_with_dq_two_effect_gamma_log, condVar = TRUE))
```
```{r}
dotplot(ranef(log_normal_model, condVar = TRUE))
```

```{r}
random_effects <- ranef(log_normal_model)
random_effects_df <- as.data.frame(random_effects$Venue)
qqPlot(random_effects_df$`(Intercept)`, 
       main = "Normal QQ Plot of Venue effect log normal model")
```

```{r}
random_effects <- ranef(log_normal_model)
random_effects_df <- as.data.frame(random_effects$Heat)
qqPlot(random_effects_df$`(Intercept)`, 
       main = "Normal QQ Plot of Heat effect log normal model")
```
```{r}
random_effects <- ranef(dash_and_hurdles_with_dq_two_effect_gamma_log)
random_effects_df <- as.data.frame(random_effects$Venue)
qqPlot(random_effects_df$`(Intercept)`, 
       main = "Normal QQ Plot of Venue effect gamma model")
```
```{r}
random_effects <- ranef(dash_and_hurdles_with_dq_two_effect_gamma_log)
random_effects_df <- as.data.frame(random_effects$Heat)
qqPlot(random_effects_df$`(Intercept)`, 
       main = "Normal QQ Plot of Heat effect gamma model")
```
